Modelling last glacial cycle ice dynamics in the Alps

### 2017-07-04 articles/cycle/alps-cycle.tex
Try to improve the record table using multirow.

\usepackage{amsmath}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}

@@

        GRIP      &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
                  &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
                  & 3238
                  & \chem{\delta^{18}O}
                  & 0.50 & $-$8.2  % -16.4126 (before scaling)
                  & \citet{Dansgaard.etal.1993} \\

        GRIP, $\Delta P$ & " & " & " & "
                  & 0.63 & $-$10.4  % -16.4126 (before scaling)
                  & " \\

        EPICA     &  75{\degree}06$^{\prime}$\,S   % 75.1
                  & 123{\degree}21$^{\prime}$\,E   % 123.35
                  & 3233
                  & \chem{\delta^{18}O}
                  & 1.05 & $-$9.7  % -9.2055
                  & \citet{Jouzel.etal.2007} \\

        EPICA, $\Delta P$ & " & " & " & "
                  & 1.33 & $-$12.2  % -9.2055
                  & " \\

        MD01-2444 &  37{\degree}34$^{\prime}$\,N   % 37.561
                  &  10{\degree}04$^{\prime}$\,W   % -10.142
                  & $-$2637
                  & \chem{U^{K'}_{37}}
                  & 1.82 & $-$7.9  % -4.345625
                  & \citet{Martrat.etal.2007} \\

        MD01-2444, $\Delta P$ & " & " & " & "
                  & 2.46 & $-$10.7  % -4.345625
                  & " \\

>>>>

\usepackage{amsmath}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}

@@

        GRIP      & \multirow{2}{*}{ 72{\degree}35$^{\prime}$\,N}   % 72.58 (decimal)
                  & \multirow{2}{*}{ 37{\degree}38$^{\prime}$\,W}   % 37.64 (decimal)
                  & \multirow{2}{*}{3238}
                  & \multirow{2}{*}{\chem{\delta^{18}O}}
                  & 0.50 & $-$8.2  % -16.4126 (before scaling)
                  & \multirow{2}{*}{\citet{Dansgaard.etal.1993}} \\

        GRIP, $\Delta P$ &&&&& 0.63 & $-$10.4 \\

        EPICA     & \multirow{2}{*}{ 75{\degree}06$^{\prime}$\,S}   % 75.1
                  & \multirow{2}{*}{123{\degree}21$^{\prime}$\,E}   % 123.35
                  & \multirow{2}{*}{3233}
                  & \multirow{2}{*}{\chem{\delta^{18}O}}
                  & 1.05 & $-$9.7  % -9.2055
                  & \multirow{2}{*}{\citet{Jouzel.etal.2007}} \\

        EPICA, $\Delta P$ &&&&& 1.33 & $-$12.2 \\

        MD01-2444 & \multirow{2}{*}{ 37{\degree}34$^{\prime}$\,N}   % 37.561
                  & \multirow{2}{*}{ 10{\degree}04$^{\prime}$\,W}   % -10.142
                  & \multirow{2}{*}{$-$2637}
                  & \multirow{2}{*}{\chem{U^{K'}_{37}}}
                  & 1.82 & $-$7.9  % -4.345625
                  & \multirow{2}{*}{\citet{Martrat.etal.2007}} \\

        MD01-2444, $\Delta P$ &&&&& 2.46 & $-$10.7 \\

        \bottomrule
      \end{tabular}}

    \end{table*}
